---
title: 
---

```{mermaid}

```

# Quantum Harmony: The Qwest for Entanglement

This document guides you through a multi-language BI and data science
journey using: - R for analysis & visualization - M for Power Query
transformations - DAX for modeling in Power BI - Python for
forecasting

----------------------------------------------------------------------

## Part 1 – R (Wrangling & Visualization)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(lubridate)
```

### Load and Inspect

```{r}
sales_data <- read_excel("quantum_sales_data.xlsx")
glimpse(sales_data)
```

### Transform

```{r}
sales_data <- sales_data %>%
  mutate(Date = as.Date(Date), Month = floor_date(Date, "month"))
```

### Summarize

```{r}
sales_summary <- sales_data %>%
  group_by(Product, Month) %>%
  summarise(Total_Sales = sum(Sales), .groups = "drop")
```

### Visualize

```{r}
ggplot(sales_summary, aes(Month, Total_Sales, color = Product)) +
  geom_line() +
  labs(title = "Sales by Product over Time") +
  theme_minimal()
```

----------------------------------------------------------------------

## Part 2 – M (Power Query Logic)

```         
let
  Source = Excel.Workbook(File.Contents("quantum_sales_data.xlsx")),
  Sheet = Source{[Name="Sheet1"]}[Content],
  Promoted = Table.PromoteHeaders(Sheet),
  Changed = Table.TransformColumnTypes(Promoted,
    {{"Date", type date}, {"Region", type text}, {"Product", type text}, {"Sales", Int64.Type}})
in
  Changed
```

----------------------------------------------------------------------

## Part 3 – DAX (Power BI Measures)

``` dax
Total Sales = SUM(Sales[Sales])

Sales Growth % =
VAR CurrentMonth = MAX(Sales[Date])
VAR PrevMonth = EDATE(CurrentMonth, -1)
VAR SalesNow = CALCULATE(SUM(Sales[Sales]), Sales[Date] = CurrentMonth)
VAR SalesPrev = CALCULATE(SUM(Sales[Sales]), Sales[Date] = PrevMonth)
RETURN DIVIDE(SalesNow - SalesPrev, SalesPrev)
```

----------------------------------------------------------------------

## Part 4 – Python (Forecasting)

```{python}
import pandas as pd
from sklearn.linear_model import LinearRegression

df = pd.read_excel("quantum_sales_data.xlsx")
df['Date'] = pd.to_datetime(df['Date'])
df['Month'] = df['Date'].dt.to_period("M").dt.to_timestamp()

df_product = df[df['Product'] == "Alpha Serum"]
monthly_sales = df_product.groupby("Month")["Sales"].sum().reset_index()
monthly_sales['Month_Num'] = (monthly_sales['Month'] - monthly_sales['Month'].min()).dt.days

X = monthly_sales[['Month_Num']]
y = monthly_sales['Sales']
model = LinearRegression().fit(X, y)

next_month = monthly_sales['Month_Num'].max() + 30
forecast = model.predict([[next_month]])
print(f"Forecast for next month: {forecast[0]:.2f}")
```

----------------------------------------------------------------------

## 🌌 Reflections

What harmonies do you notice between R, Python, M, and DAX? How does
each language complement the others in your workflow?

